% FAQs Chapter
\chapter{Frequently Asked Questions}

\section{General Questions}

\textbf{Q: Do I need both apps to use the system?}

A: Not necessarily. You can use pre-trained models in the Prediction App without using the Training App. However, for custom forecasts, you'll need to train your own models.

\textbf{Q: Can I retrain models?}

A: Yes. You can retrain models at any time using the Training App. We recommend quarterly retraining for optimal accuracy.

\textbf{Q: Is internet required for both apps?}

A: The Training App needs internet only for initial setup. The Prediction App requires continuous internet connection since it's cloud-based.

\textbf{Q: How secure is my data?}

A: Data uploaded to the Training App remains local. The Prediction App processes data temporarily in session only.

\section{Technical Questions}

\textbf{Q: What's the maximum data size I can upload?}

A: Training App: Limited by your local system resources. Prediction App: Models up to 50MB. CSV files up to 200MB.

\textbf{Q: Why do my forecasts differ from expectation?}

A: Several factors affect forecasts:
\begin{itemize}
	\item Data quality and completeness
	\item Model selection
	\item Hyperparameter settings
	\item Unexpected market changes
\end{itemize}

\textbf{Q: Can I use different date formats?}

A: No. Use YYYY-MM-DD format only for all date fields.

\textbf{Q: Where are models stored?}

A: Training App: \verb|models/default/| directory locally. Prediction App: Temporary session storage.

\section{Usage Questions}

\textbf{Q: How often should I retrain models?}

A: Recommend quarterly retraining or when accuracy drops below acceptable levels.

\textbf{Q: Can I forecast for specific stores?}

A: Currently, the system provides aggregate forecasts. Individual store forecasting may be added in future versions.

\textbf{Q: What happens to my data after session ends?}

A: Session data is automatically cleared. Download important forecasts before closing.

\textbf{Q: Can I use the system offline?}

A: Training App: Yes, after initial setup. Prediction App: No, requires internet connection.

\section{Model Questions}

\textbf{Q: Which model should I choose?}

A: Start with Exponential Smoothing for simplicity. Use Auto ARIMA for complex patterns.

\textbf{Q: How do I improve model accuracy?}

A: Consider:
\begin{itemize}
	\item More historical data
	\item Data cleaning and preprocessing
	\item Parameter tuning
	\item Different model selection
\end{itemize}

\textbf{Q: Can I combine multiple models?}

A: Not directly in the current version. Consider averaging results manually.

\section{Troubleshooting FAQs}

\textbf{Q: My model won't save. What to do?}

A: Check write permissions for the models/default/ directory. Ensure sufficient disk space.

\textbf{Q: Prediction App shows 'session expired'. Fix?}

A: Reload the page and re-upload your model. Sessions timeout after 30 minutes of inactivity.

\textbf{Q: Training is very slow. Normal?}

A: Auto ARIMA can take significant time. Reduce max parameters or switch to Exponential Smoothing.

\section{Advanced Usage}

\textbf{Q: Can I automate the process?}

A: Advanced users can script interactions with the Training App. Prediction App requires manual interaction.

\textbf{Q: Where do I find logs?}

A: Training App: Console output during runtime. Prediction App: Browser developer console (F12).

\textbf{Q: Can I extend the system?}

A: The Training App is open for local modifications. Prediction App is hosted and requires different architecture.

\section{Support Questions}

\textbf{Q: Where to report bugs?}

A: Contact support@walmart-forecasting.example.com with detailed error information.

\textbf{Q: Will there be updates?}

A: System undergoes regular updates. Major changes announced in documentation.

\textbf{Q: Training materials available?}

A: This manual, plus optional video tutorials and documentation examples.